Analysis, Prototyping and Locomotion Control of a Quadruped Robot\\

### 2023-08-31 LARS_paper/paper.tex
Update authors, add caramel github reference and remove last figure

%TODO
\author{\IEEEauthorblockN{1\textsuperscript{st} Lucas Souza}
  \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
    \textit{name of organization (of Aff.)}\\
    Salvador, Brasil \\
    lucaslinssouza@gmail.com}
  \and
  \IEEEauthorblockN{2\textsuperscript{nd} Felipe Mohr}
  \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
    \textit{name of organization (of Aff.)}\\
    Salvador, Brasil \\
    email address or ORCID}
  \and
  \IEEEauthorblockN{3\textsuperscript{rd} Brenda Alencar}
  \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
    \textit{name of organization (of Aff.)}\\
     Salvador, Brasil \\
    brenda.s1602@outlook.com}
}

@@

\begin{figure}[!b]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{plane_boxplot.png}
    \caption{Flat terrain.}
    \label{fig:imu_test_plane}
  \end{subfigure}
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{irregular_boxplot.png}
    \caption{Uneven terrain.}
    \label{fig:imu_test_irregular}
  \end{subfigure}
  \caption{Robot body's oscillation in both terrains.}
  \label{fig:imu_test}
  % \vspace{-1.5\baselineskip}
\end{figure}

@@

\begin{table}[b]
  \centering
  \caption{Angular velocity and stability results.}
  \scalebox{1.3}{
  \begin{tabular}{ccc}
    \hline
    \textbf{Test}              & \textbf{1}   & \textbf{2}   \\ \hline
    Ter.                       & Uneven       & Uneven       \\ \hline
    \begin{tabular}[c]{@{}c@{}}S. C. \end{tabular} & No           & Yes          \\ \hline
    \begin{tabular}[c]{@{}c@{}}Angular vel. \\ $(rad/s)$ \end{tabular} & 0.19         & 0.19         \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Ang. Vel.}$  \\ $(rad/s)$ \end{tabular} & 0.006        & 0.007        \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Roll}$ \end{tabular} & 16.16\degree & 16.84\degree \\\hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Roll}$ \end{tabular} & 1.88\degree  & 2.6\degree  \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Pitch}$ \end{tabular} & 11.79\degree & 12.89\degree \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Pitch}$ \end{tabular} & 1.05\degree  & 1.41\degree  \\ \hline
  \end{tabular}
  }
  \label{tab:ang_vel_stab}
  % \vspace{-\baselineskip}
\end{table}

\begin{figure}[!b]
  \centering
  \includegraphics[width=0.5\textwidth]{ang_vel_boxplot.png}
  \caption{Robot body's oscillation during yaw motion.}
  \label{fig:ang_vel_boxplot}
  % \vspace{-1.5\baselineskip}
\end{figure}

@@

The robot's project is open source and is available on GitHub [Blinded reference]. % \cite{CaramelRepo}.

>>>>

%TODO
\author{\IEEEauthorblockN{1\textsuperscript{st} Lucas Souza}
  \IEEEauthorblockA{\textit{Departament of Robotics} \\
    \textit{SENAI CIMATEC}\\
    Salvador, Brazil \\
    lucaslinssouza@gmail.com}
  \and
  \IEEEauthorblockN{2\textsuperscript{nd} Felipe Mohr}
  \IEEEauthorblockA{\textit{Departament of Robotics} \\
    \textit{SENAI CIMATEC}\\
    Salvador, Brazil \\
    felipe18mohr@gmail.com}
  \and
  \IEEEauthorblockN{3\textsuperscript{rd} Brenda Alencar}
  \IEEEauthorblockA{\textit{Departament of Robotics} \\
    \textit{SENAI CIMATEC}\\
     Salvador, Brazil \\
    brenda.s1602@outlook.com}
}

@@

\begin{figure}[!tb]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{plane_boxplot.png}
    \caption{Flat terrain.}
    \label{fig:imu_test_plane}
  \end{subfigure}
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{irregular_boxplot.png}
    \caption{Uneven terrain.}
    \label{fig:imu_test_irregular}
  \end{subfigure}
  \caption{Robot body's oscillation in both terrains.}
  \label{fig:imu_test}
  % \vspace{-1.5\baselineskip}
\end{figure}

@@

\begin{table}[tb]
  \centering
  \caption{Angular velocity and stability results.}
  \scalebox{1.3}{
  \begin{tabular}{ccc}
    \hline
    \textbf{Test}              & \textbf{1}   & \textbf{2}   \\ \hline
    Ter.                       & Uneven       & Uneven       \\ \hline
    \begin{tabular}[c]{@{}c@{}}S. C. \end{tabular} & No           & Yes          \\ \hline
    \begin{tabular}[c]{@{}c@{}}Angular vel. \\ $(rad/s)$ \end{tabular} & 0.19         & 0.19         \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Ang. Vel.}$  \\ $(rad/s)$ \end{tabular} & 0.006        & 0.007        \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Roll}$ \end{tabular} & 16.16\degree & 16.84\degree \\\hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Roll}$ \end{tabular} & 1.88\degree  & 2.6\degree  \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Pitch}$ \end{tabular} & 11.79\degree & 12.89\degree \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Pitch}$ \end{tabular} & 1.05\degree  & 1.41\degree  \\ \hline
  \end{tabular}
  }
  \label{tab:ang_vel_stab}
  % \vspace{-\baselineskip}
\end{table}

% \begin{figure}[!tb]
%   \centering
%   \includegraphics[width=0.5\textwidth]{ang_vel_boxplot.png}
%   \caption{Robot body's oscillation during yaw motion.}
%   \label{fig:ang_vel_boxplot}
%   % \vspace{-1.5\baselineskip}
% \end{figure}

@@

The robot's project is open source and is available on GitHub \cite{CaramelRepo}.
